Predict Models

### 2024-01-04 scripts/predict_models.Rmd
more rfe subset logic

  return(layer_subset)
  #terra::predict(
  #  type = 'prob', cores = 16,
  #  layer_subset, sdm, cpkgs="randomForest",
  #  filename = file.path(pout, paste0(x$species, '.tif')),
  #  wopt = c(names = 'predicted_suitability'))

>>>>

  return(layer_subset)
  surface <- terra::subset(terra::predict(
    layer_subset, sdm, cpkgs="randomForest",
    type = 'prob', cores = 16,
    wopt = c(names = 'predicted_suitability'))
  , 2)
  names(surface) <- 'Hyp.Suitability'
  writeRaster(surface, filename = file.path(pout, paste0(x$species, '.tif')))
